\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemNormal}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubtitle}[2]{
  \vspace{-1pt}
    \begin{tabular*}{0.97\textwidth}
    {l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Nguyen Van Trung Hieu}} & Email :{pekonsaysua@gmail.com}\\
  {https://linkedin.com/in/hieujoey99} & Mobile : +84 982 693 899 \\
\end{tabular*}

% %-----------SUMMARY-----------------
% \section{Summary}
%     I’m a Full Stack Software Engineer with 3 years of experience in Web and Mobile App Development. I always try to complete every work with enthusiasm and passion. I also spend time learning new technologies and best practices to become a better engineer.

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Hanoi University of Science and Technology}{Hanoi, Vietnam}
      {Engineer of Computer Science;  Classification: Very good}{Aug. 2017 -- Mar. 2022}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Authentic Education Hub}{Hanoi, Vietnam}
      {Mobile Developer}{Apr 2024 - Present}
      \resumeItemListStart
        \resumeItem{Chat}
          {Implemented a real-time chat feature and AI-powered chat assistant. Realtime-time chat using socket and support user send message with text, image, video and can react and reply message. Integrated FCM for push notifications.}
        \resumeItem{Statistics}
          {Use tables and charts to collect statistics on student progress during the learning process on the LMS system.}
      \resumeItemListEnd

    \resumeSubheading
      {VDSMART, JSC}{Hanoi, Vietnam}
      {Frontend Team Lead}{Jun 2023 - Mar 2024}
      \resumeItemListStart
        \resumeItem{Product}
          {Yoga practice application with AI technology to support user.}
        \resumeItem{Responsibilities}
          {Working directly with another team to define product feature, evaluating front-end technologies, reviewing code and support team member.}
        \resumeItem{Backend}
          {Integrate with video streaming systems to distribute yoga exercises. Integrate purchasing of exercises through the ERP system.}
        \resumeItem{Mobile}
          {Write code for a library that can be integrated with mobile applications, used as a virtual assistant to support Yoga practice through images and sounds along with videos of Yoga exercises.}
      \resumeItemListEnd
    \resumeSubtitle
      {Project Director}{Dec 2021 - Dec 2022}
      \resumeItemListStart
        \resumeItem{Project}
          {Smart Library - system replaces the traditional library at HCMA.}
        \resumeItem{Responsibilities}
          {Participate in writing technical design document of project; meeting and exchange information with relevant parties; deploying and testing software at client site.}
        \resumeItem{System}
          {Build a user store system, allowing other systems log in via Single Sign-On. Integrate systems: SSO Authentication, Face Authentication, Smart Library, Electronic Library, Heatmap.}
        \resumeItem{Frontend}
          {Develop terminal applications for students: Smartlib Mobile - application to access digital resources in the library, including pdf, video and audio books; Smartlib Kiosk - application runs ads on Kiosk screens, which can automatically adjust based on the identity of the user standing in front of the Kiosk.}
      \resumeItemListEnd
    \resumeSubtitle
      {Frontend Developer}{Apr 2021 - Dec 2021}
      \resumeItemListStart
        \resumeItem{Responsibilities}
          {Write technical documents for Smart School Project - State-level topic (KC-4.0/19-25 Program); develop software in Smart School and EyePro Cloud projects.}
        \resumeItem{School Management System}
          {Build a school management system, including backend, web admin and mobile app.}
        \resumeItem{Learning Management System}
          {Integrate Chatbot feature to warn users early about progress and learning results.}
        \resumeItem{Adaptive Learning System}
          {Develop mobile applications that connect to the backend to access digital coursewares; integrate coursewares recommendation system.}
        \resumeItem{EyePro Cloud}
          {Develop web admin and mobile application to monitor users in the room using cameras for monitoring.}
      \resumeItemListEnd

    % \resumeSubheading
    %   {Lucena Research}{Atlanta, GA}
    %   {Data Scientist}{Summer 2012 and 2013}
    %   \resumeItemListStart
    %     \resumeItem{Portfolio Management}
    %       {Created models for portfolio hedging,  portfolio optimization and price forecasting. Also creating a strategy backtesting engine used for simulating and backtesting strategies.}
    %     \resumeItem{QuantDesk}
    %       {Python backend for a web application used by hedge fund managers for portfolio management.}
    %   \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{TanyenMart}
      {Freelance Project - Market application, allows users to buy and sell.}
    \resumeSubItem{SmartCard}
      {Freelance Project - E-wallet application, support money transfer, deposit, withdrawal.}
    \resumeSubItem{Fitness App}
      {Social fitness network app.}
    \resumeSubItem{Fakebook App}
      {Social network app.}
    \resumeSubItem{Ecommerce App}
      {An app that helps customer make purchases and vendor post products,
payment support via Stripe.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Dart, Kotlin, Javascript, Python, PHP}
     \hfill
     \textbf{Technologies}{: Flutter, Firebase, React, NodeJS}
   }
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
